The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
abstract edits

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. Multilayer networks
promise the integration of monolayer animal social networks with the complexity
and importance of animal space use and movement in heterogeneous landscapes.
Despite the complex interplay between social networks and how animals use space,
there remains an important biological and methodological gap in our
understanding of an animal’s perception of scale. But scale can affect
multilayer network dynamics and how we build and interpret them. Here we discuss
the role of scale in the context of multilayer networks and provide a social
ungulate case study to illustrate the role of social, spatial, and temporal
scale on multilayer processes. We also present perspectives on future
development and application of scale in multilayer networks with respect to:
habitat selection and space use; phenotypes and individual fitness; and movement
ecology and collective movement. Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research; our contribution
incorporates perspectives on how the social environment and spatial processes
are linked across scales in a multilayer

>>>>

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. <!-- TODO: add temporal scale --> Multilayer networks
promise the integration of monolayer animal social networks with the complexity
and importance of animal space use and movement in heterogeneous landscapes.
Despite the complex interplay between social networks and how animals use space,
there remains an important biological and methodological gap in our
understanding of an animal’s perception of scale. Here we discuss
the role of scale in the context of multilayer networks and provide a social
ungulate case study to illustrate the role of social, spatial, and temporal
scale on multilayer processes. We also present perspectives on future
development and application of scale in multilayer networks with respect to:
habitat selection and space use; phenotypes and individual fitness; and movement
ecology and collective movement. Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research, as such our contribution
incorporates perspectives on how the social environment and spatial processes
are linked across scales in a multilayer context.
